Forecasting the US Presidential Election: A Poll-of-Polls Approach Using Linear Models By Using Data of Pollsters From Five Thirty Eight In 2024

### 2024-10-23 paper/paper.qmd
remove some code from starter folder, add references

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

# ggplot(penguins, aes(x = island, fill = species)) +
#   geom_bar(alpha = 0.8) +
#   scale_fill_manual(values = c("darkorange","purple","cyan4"),
#                     guide = "none") +
#   theme_minimal() +
#   facet_wrap(~species, ncol = 1) +
#   coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

# analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
# 
# analysis_data |> 
#   ggplot(aes(x = width, y = length)) +
#   geom_point(alpha = 0.8) +
#   theme_minimal() +
#   labs(x = "Wing width (mm)",
#        y = "Wing length (mm)")
```

Talk way more about it.

@@

Response Variable is pct. Predictors are log(sample_size), pollscore, numeric_grade, transparency_score, and days_since_start, detail can be found in [@sec-octvar], and [@sec-prevar]

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use priors $\text{Normal}(0, 5)$ to allow for more flexibility of predictors effects with “autoscale = TRUE”. Then we crate a data frame like [@tbl-newdata], we set the quality scale of predict data to the best to perform a poll that has high quality. the result is shown as [@sec-splresult]
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-newdata

@@

# Plot the spline fit
ggplot(combined_data, aes(x = days_since_start, y = pct, color = pollster)) +
  # DEM predictions
  geom_line(
    data = pred_summary %>% filter(party == "DEM"),
    aes(x = days_since_start, y = pred_mean_dem, color = "DEM"),
    inherit.aes = FALSE
  ) +
  geom_ribbon(
    data = pred_summary %>% filter(party == "DEM"),
    aes(x = days_since_start, ymin = pred_lower_dem, ymax = pred_upper_dem, fill = "DEM"),
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  # REP predictions
  geom_line(
    data = pred_summary %>% filter(party == "REP"),
    aes(x = days_since_start, y = pred_mean_rep, color = "REP"),  # Move color inside aes()
    inherit.aes = FALSE
  ) +
  geom_ribbon(
    data = pred_summary %>% filter(party == "REP"),
    aes(x = days_since_start, ymin = pred_lower_rep, ymax = pred_upper_rep, fill = "REP"),  # Move fill inside aes()
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  # Use scale_color_manual and scale_fill_manual for colors and fills
  scale_color_manual(values = c("DEM" = "blue", "REP" = "red"), 
                     name = "Party",
                     labels = c("DEM (Blue)", "REP (Red)")) +
  scale_fill_manual(values = c("DEM" = "blue", "REP" = "red"), 
                    name = "Party",
                    labels = c("DEM (Blue)", "REP (Red)")) +
  labs(
    x = "Days since 2024",
    y = "Percentage",
  ) +
  theme_minimal()
```
The prediction graph contains prediction of spline fit model for two parties, blue line represents the DEM party's predicted percentage of support, and the red line represents the REP party's predicted percentage of support over time (measured in days since the start of 2024). We can tell that the predict support of DEM party is taking the lead by aroud 2 percent until the last day of the dataset.

>>>>

@@

Response Variable is pct. Predictors are log(sample_size), pollscore, numeric_grade, transparency_score, and days_since_start, detail can be find in [@sec-octvar], and [@sec-prevar]

@@

We run the model in R [@citeR] using the `rstanarm` package of [@rstanarm]. We use priors $\text{Normal}(0, 5)$ to allow for more flexibility of predictors effects with “autoscale = TRUE”. Then we crate a data frame like [@tbl-newdata], we set the quality scale of predict data to the best to perform a poll that has high quality. the result is shown as [@sec-splresult]
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-newdata

@@

# Plot the spline fit
ggplot(combined_data, aes(x = days_since_start, y = pct, color = pollster)) +
  # DEM predictions
  geom_line(
    data = pred_summary %>% filter(party == "DEM"),
    aes(x = days_since_start, y = pred_mean_dem, color = "DEM"),
    inherit.aes = FALSE
  ) +
  geom_ribbon(
    data = pred_summary %>% filter(party == "DEM"),
    aes(x = days_since_start, ymin = pred_lower_dem, ymax = pred_upper_dem, fill = "DEM"),
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  # REP predictions
  geom_line(
    data = pred_summary %>% filter(party == "REP"),
    aes(x = days_since_start, y = pred_mean_rep, color = "REP"),  # Move color inside aes()
    inherit.aes = FALSE
  ) +
  geom_ribbon(
    data = pred_summary %>% filter(party == "REP"),
    aes(x = days_since_start, ymin = pred_lower_rep, ymax = pred_upper_rep, fill = "REP"),  # Move fill inside aes()
    alpha = 0.2,
    inherit.aes = FALSE
  ) +
  # Use scale_color_manual and scale_fill_manual for colors and fills
  scale_color_manual(values = c("DEM" = "blue", "REP" = "red"), 
                     name = "Party",
                     labels = c("DEM (Blue)", "REP (Red)")) +
  scale_fill_manual(values = c("DEM" = "blue", "REP" = "red"), 
                    name = "Party",
                    labels = c("DEM (Blue)", "REP (Red)")) +
  labs(
    x = "Days since 2024",
    y = "Percentage",
  ) +
  theme_minimal()
```
The prediction graph [@fig-splpredict] contains prediction of spline fit model for two parties, blue line represents the DEM party's predicted percentage of support, and the red line represents the REP party's predicted percentage of support over time (measured in days since the start of 2024). We can tell that the predicted support of DEM party is taking the lead by aroud 2 percent until the last day of the dataset.
